\SW Extended! Snappy Titles!

### 2015-05-26 doc/sw-extended.tex
added figure placeholder

\subsection{The Online System}
\label{sec:formalism:online}
In \sw, this is fixed at $2 \times 10^{-4}$, or the expectation that
around 100 lenses will be found in 430,000 images. Because \sw is an online
system that constantly reevaluates most of the above parameters (except $p_0$
and any non-blank $C_{ij}$) in order to promote likely lenses\footnote{Note
that this does not change the probability that a volunteer will actually draw
said image.} or to retire likely duds,\footnote{Images whose probability of
being a lens drops below a certain threshold are removed from the active
dataset.} we augment $p$, $PL$, and $PD$ as $p_j^k$, the evaluation of
$p_j$ at time $k$. \sw uses Bayes' Theorem to update $p_j^{(k + 1)}$ for
some new evaluation $C_{ij}$\footnote{There is no superscript for $C_{ij}$
because each user only sees an image once.}:
\begin{align}
  p_j^{(k + 1)} &= \left ( \frac{C_{ij} PL_{i}^{k}
  }{PL_{i}^{k} p_j^k + (1 - PD_{i}^{k})(1 -
  p_j^k)}
  \right. \notag \\ & \; \left . +
  \frac{(1 - C_{ij}) (1 - PL_{i}^{k})
  }{(1 - PL_{i}^{k}) p_j^k + PD_{i}^{k}(1 -
  p_j^k)} \right ) p_j^k \ ,
\end{align}
The first term on the right hand side is the probability update for evaluating
the object to be a lens, while the second term is the probability that the
image is a lens if the volunteer evaluates it to be a dud.  (For example, an
obtuse volunteer who always perfectly incorrectly classifies an image will
actually change the probability exactly the same as one who always perfectly
correctly classifies an image, given that the estimate of the obtuse
volunteer's skill ($PL_{i} = 0$) is accurate.)

@@

\subsubsection{E-Step}
\label{sec:formalism:em:estep}
% TODO: reword. The maximization here is over the zj's, so word to make that clear.
% The E-Step is just taking the expected complete log-likelihood, or the
% expectation value over $P(\cdot \ | x, \phi)$.
The E-Step is maximizing the complete log-likelihood with respect to the image
probability $p_j$.  This is equivalent to replacing $z_j$ with $p_j$:
% TODO: replace this with equivalent like eq1
\begin{align}
  p_j &= \frac{1}{N_j} \sum_{i \in \Omega_j} P(z_j = 1 \ | \ C_{ij} ; \Phi) =
  \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ P(C_{ij} \ | \ z_j = 1; \Phi)
P(z_j = 1 ; \Phi)}{P(C_{ij} ; \Phi)} \\
&= \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ PL_{i}^{C_{ij}} (1 - PL_{i})^{(1 -
C_{ij})} p_{ij}^{0}}{ PL_{i}^{C_{ij}} (1 -
  PL_{i})^{(1 - C_{ij})} p_{ij}^{0} + PD_{i}^{(1 - C_{ij})} (1 -
PD_{i})^{C_{ij}} (1 - p_{ij}^{0})}
\end{align}
where $i \in \Omega_j$ is now the set of classifications done on the $j$-th
image and $N_j$ is the number of classifications done on the $j$-th image. This
makes sense: $p_{ij}^{0}$ is just the prior likelihood of an image being a lens,
while $PL_{i}$ is how well we would have identified a lens as such.

@@

An easy way to conceptualize the previous section is to note that the
Expectation Maximization takes advantage of the fact that each classification
is supposed to be independent of the others and so can be treated as though all
classifications were made at the same time.  The repetition of the steps
ensures that the parameters are self-consistent.

@@

\subsection{Validation of Training}
\label{sec:validation}

A validation dataset is needed to prevent overfitting training data and to try
to test how the training data does against real lenses. These need to come in
two categories: actual lens environments, and simulated lenses. The need for
two sets arises because of the paucity of actual lenses. In \SW, most training
objects are explicitly given to a user -- if a user incorrectly identifies a
training object, they are informed of that failure, and likewise for a correct
classification.

@@

We can extend the \SW binomial model to include multiple classifications and
multiple categories -- we can talk about things like $P(``1" | \rm{LENSED\
QUASAR})$ where a user assigns an object a rank $"1"$ and wish to know the
likelihood that a lensed quasar would yield that category.

@@

Now we repeat the exercise earlier of computing the expected complete log
likelihood under the conditional distribution $p(z_{j} | C_{ij}; p^0,
P_{i})$. Call $p_{jv} = p(z_{jv} | C_{iju}; p^0_{jv}, P_{ivu})$. It is
sufficient to compute $p_{jv}$ to complete this step. By Bayes's Rule, we
know that
\flag{Chris}{Is this an abuse of notation? I want for a single $z_{jv}$, but
given $C_{iju}, p^0_{jv}, P_{ivu}$ for \textit{all} $i$ and $u$. So really it
is more correct to say $ p(z_{jv}) \prod_i \prod_u p(C_{iju} | z_{jv}; p^0_{jv},
P_{ivu})$ since each classification $C_{ij}$ is independent. Should I do that?
Alternatively, I could put one of those $\cdot$ in place of each $i$ and $u$...}
$$
p(z_{jv} | C_{iju}; p^0_{jv}, P_{ivu}) \propto p(C_{iju} | z_{jv}; p^0_{jv},
P_{ivu}) p(z_{jv})
$$
But we know the values of all these terms, so we find:
\todo{Chris}{Double check this. I'm not sure it's strictly correct when you
have more than one classification per image / type.}
\begin{align}
  p_{jv} = \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{\prod_u p^0_{jv}
  P_{ivu}^{C_{iju}}}{\sum_{v'} \prod_u p^0_{jv'} P_{iv'u}^{C_{iju}}}
\end{align}

@@

Like in the binomial case, the multinomial case can be performed online, where
each new piece of information updates an existing assessment of lens
classification and user skill. If a new classification $C_{iju}^{(k + 1)}$ is
made, then by Bayes' Theorem the updates are as follows (with $i$, $j$, $u$,
and $v$ acting as fixed indices):
\begin{align}
  p_{jv}^{(k + 1)} &= \left( \frac{P^{k}_{ivu}^{C_{iju}^{(k + 1)}}}{\sum_{v'}
  p_{jv'}^{k} P^{k}_{iv'u}^{C_{iju}^{(k+1)}}} \right) p_{jv}^{k} \\
  P^{(k+1)}_{ivu}  &= \frac{C^{(k+1)}_{iju} p^{k}_{jv} + P^{k}_{ivu} \sum_{j'\in
  \Omega_i} p^{k}_{j'v} }{p^{k}_{jv} + \sum_{j'
  \in \Omega_i} p^{k}_{j'v}}
\end{align}
If we are using only a supervised learning set, then $p^k_{j'v} \in (0, 1)$.

@@

\section{Dynamic Allocations}
\todo{Chris}{This section will examine whether we would be better off
  dynamically assigning images to people (based on current estimates of skill
  and probability) rather than randomly assigning them. This means I will need
  to create some sort of 'SpaceWarps Emulator'. (Actually, the other thing
  I can do is use the blacklist developed earlier to throw out
  contributions in an informed manner in order to construct different
  simulations.) Before I even do that, another
aspect I would like to examine and is probably useful is whether we can
reliably identify skilled users early on. That is, instead of looking at final
skill vs effort, look at many trajectories of skill vs effort over time. That
would be a useful thing to show to prove that we can find the good users in the
first place -- early on!}

>>>>

\subsection{The Online System}
\label{sec:formalism:online}
In \sw, this is fixed at $2 \times 10^{-4}$, or the expectation that
around 100 lenses will be found in 430,000 images. Because \sw is an online
system that constantly reevaluates most of the above parameters (except $p_0$
and any non-blank $C_{ij}$) in order to promote likely lenses\footnote{Note
that this does not change the probability that a volunteer will actually draw
said image.} or to retire likely duds,\footnote{Images whose probability of
being a lens drops below a certain threshold are removed from the active
dataset.} we augment $p$, $PL$, and $PD$ as $p_j^k$, the evaluation of
$p_j$ at time $k$. \sw uses Bayes's Theorem to update $p_j^{(k + 1)}$ for
some new evaluation $C_{ij}$\footnote{There is no superscript for $C_{ij}$
because each user only sees an image once.}:
\begin{align}
  p_j^{(k + 1)} &= \left ( \frac{C_{ij} PL_{i}^{k}
  }{PL_{i}^{k} p_j^k + (1 - PD_{i}^{k})(1 -
  p_j^k)}
  \right. \notag \\ & \; \left . +
  \frac{(1 - C_{ij}) (1 - PL_{i}^{k})
  }{(1 - PL_{i}^{k}) p_j^k + PD_{i}^{k}(1 -
  p_j^k)} \right ) p_j^k \ ,
\end{align}
The first term on the right hand side is the probability update for evaluating
the object to be a lens, while the second term is the probability that the
image is a lens if the volunteer evaluates it to be a dud.  (For example, an
obtuse volunteer who always perfectly incorrectly classifies an image will
actually change the probability exactly the same as one who always perfectly
correctly classifies an image, given that the estimate of the obtuse
volunteer's skill ($PL_{i} = 0$) is accurate.)

@@

\subsubsection{E-Step}
\label{sec:formalism:em:estep}
\todo{Chris}{reword. The maximization here is over the zj's, so word to
  make that clear. The E-Step is just taking the expected complete
log-likelihood, or the expectation value over $P(\cdot \ | x, \phi)$.}
The E-Step is maximizing the complete log-likelihood with respect to the image
probability $p_j$.  This is equivalent to replacing binary $z_j$ with
probability $p_j$:
\todo{Chris}{replace this with equivalent like eq1}
\begin{align}
  p_j &= \frac{1}{N_j} \sum_{i \in \Omega_j} P(z_j = 1 \ | \ C_{ij} ; \Phi) =
  \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ P(C_{ij} \ | \ z_j = 1; \Phi)
P(z_j = 1 ; \Phi)}{P(C_{ij} ; \Phi)} \\
&= \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ PL_{i}^{C_{ij}} (1 - PL_{i})^{(1 -
C_{ij})} p_{ij}^{0}}{ PL_{i}^{C_{ij}} (1 -
  PL_{i})^{(1 - C_{ij})} p_{ij}^{0} + PD_{i}^{(1 - C_{ij})} (1 -
PD_{i})^{C_{ij}} (1 - p_{ij}^{0})}
\end{align}
where $i \in \Omega_j$ is now the set of classifications done on the $j$-th
image and $N_j$ is the number of classifications done on the $j$-th image. This
makes sense: $p_{ij}^{0}$ is just the prior likelihood of an image being a lens,
while $PL_{i}$ is how well we would have identified a lens as such.

@@

An easy way to conceptualize this section is to note that the Expectation
Maximization takes advantage of the fact that each classification is supposed
to be independent of the others and so the dataset can be treated as though all
classifications were made at the same time.  The repetition of the $E$ and $M$
steps ensures that the parameters are self-consistent.

@@

\section{Tests}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{Offline vs online}

\flag{Chris}{This section was somewhat talked about in \SW paper 1, but it
needs reiterating here.}

\begin{figure}
\begin{center}
    \includegraphics[scale=]{Figures/}
\end{center}
\caption{ROC curve of online vs offline for both stages}
\label{fig:}
\end{figure}

\begin{figure}
\begin{center}
    \includegraphics[scale=]{Figures/}
\end{center}
\caption{Scatter plot of p values from online and offline for both stage 1 and
stage 2. Then a second plot of a similar thing but for the confusion matrices.
Show if there are any systematic differences that need to be explained}
\label{fig:}
\end{figure}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{Unsupervised vs supervised}

\begin{figure}
\begin{center}
    \includegraphics[scale=]{Figures/}
\end{center}
\caption{This figure will show three sets of ROC curves: supervised only,
unsupervised only, and both together.}
\label{fig:}
\end{figure}

\begin{figure}
\begin{center}
    \includegraphics[scale=]{Figures/}
\end{center}
\caption{Scatter plot of p values using supervised only vs unsupervised +
supervised and unsupervised only. Then a second plot of a similar thing but for
the confusion matrices. The idea is to show that (probably) there is no major
systematic shift in evaluations.}
\label{fig:}
\end{figure}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{Importance of initialization}

\begin{figure}
\begin{center}
    \includegraphics[scale=]{Figures/}
\end{center}
\caption{This figure will show ROC curves for different initialization parameters.}
\label{fig:}
\end{figure}

\begin{figure}
\begin{center}
    \includegraphics[scale=]{Figures/}
\end{center}
\caption{Scatter plot of p values. Then a second plot of a similar thing but for
the confusion matrices. The idea is to show that (probably) there is no major
systematic shift in evaluations.}
\label{fig:}
\end{figure}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{Simulated vs known strong lenses}

\flag{Chris}{This section will talk about training on the small set of known
  strong lenses.  I cut down the users only to those who observed strong
  lenses. I could use as a prior the distribution of confusion matrices and
  probabilities from the training, or maybe some sort of dirichlet model. I
think it will be vital that I use an informative prior, since in my previous
explorations of this matter there simply wasn't enough data to go off of.}

\section{Extensions to Existing Model}

@@

We can extend the \SW binomial model to include multiple classifications and
multiple categories -- we can talk about things like $P(``1" | \rm{LENSED\
QUASAR})$ where a user assigns an object a rank $``1"$ and wish to know the
likelihood that a lensed quasar would yield that category.

@@

Now we repeat the exercise earlier of computing the expected complete log
likelihood under the conditional distribution $p(z_{j} | C_{ij}; p^0,
P_{i})$. Call $p_{jv} = p(z_{jv} | C_{iju}; p^0_{jv}, P_{ivu})$. It is
sufficient to compute $p_{jv}$ to compute this step. By Bayes's Theorem, we
know that
\flag{Chris}{Is this an abuse of notation? I want for a single $z_{jv}$, but
given $C_{iju}, p^0_{jv}, P_{ivu}$ for \textit{all} $i$ and $u$. So really it
is more correct to say $ p(z_{jv}) \prod_i \prod_u p(C_{iju} | z_{jv}; p^0_{jv},
P_{ivu})$ since each classification $C_{ij}$ is independent. Should I do that?
Alternatively, I could put one of those $\cdot$ in place of each $i$ and $u$...}
$$
p(z_{jv} | C_{iju}; p^0_{jv}, P_{ivu}) \propto p(C_{iju} | z_{jv}; p^0_{jv},
P_{ivu}) p(z_{jv})
$$
But we know the values of all these terms, so we find:
\todo{Chris}{Double check this. I'm not sure it's strictly correct when you
have more than one classification per image / type.}
\begin{align}
  p_{jv} = \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{\prod_u p^0_{jv}
  P_{ivu}^{C_{iju}}}{\sum_{v'} \prod_u p^0_{jv'} P_{iv'u}^{C_{iju}}}
\end{align}
where $N_j = \sum_{i \in \Omega_j} 1$.

@@

Like in the binomial case, the multinomial case can be performed online, where
each new piece of information updates an existing assessment of lens
classification and user skill. If a new classification $C_{iju}^{(k + 1)}$ is
made, then by Bayes's Theorem the updates are as follows (with $i$, $j$, $u$,
and $v$ acting as fixed indices):
\question{Chris}{In our case, there is only one classification $u$ such that
  $C_{iju'} = 1$ if $u' = u$ and $0$ else. Is it more clear if I instead call
our classification $C_{ij}$ and multiply over all $u$ indices?}
\todo{Chris}{Double check whether the updates to $p$ and $P$ use the $k+1$ term
of the other, and if so, the ordering of it.}
\begin{align}
  p_{jv}^{(k + 1)} &= \left( \frac{P^{k}_{ivu}^{C_{iju}^{(k + 1)}}}{\sum_{v'}
  p_{jv'}^{k} P^{k}_{iv'u}^{C_{iju}^{(k+1)}}} \right) p_{jv}^{k} \\
  P^{(k+1)}_{ivu}  &= \frac{C^{(k+1)}_{iju} p^{k}_{jv} + P^{k}_{ivu} \sum_{j'\in
  \Omega_i} p^{k}_{j'v} }{p^{k}_{jv} + \sum_{j'
  \in \Omega_i} p^{k}_{j'v}} \\
  P^{(k+1)}_{ivu}  &= \left( \frac{p^{k}_{jv}}{p^{k}_{jv} + \sum_{j'
  \in \Omega_i} p^{k}_{j'v}} \right) C^{(k+1)}_{iju} +
  \left( \frac{\sum_{j'\in \Omega_i} p^{k}_{j'v}}
    {p^{k}_{jv} + \sum_{j'\in \Omega_i} p^{k}_{j'v}}
 \right) P^{k}_{ivu} \end{align}
\question{Chris}{Do we like the first or second way of writing out
$P^{(k+1)}_{ivu}$?}
If we are using only a supervised learning set, then $p^k_{jv} \in (0, 1)$, and
$\Omega_i$ becomes instead of the set of all images classified by user $i$ the
set of all training images classified by user $i$.
\todo{Chris}{Put in the Laplace smoothing. Double check that it again is just
$M$ and $2M$ in the numerator and denominator, respectively.}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{The Prior}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{Validation of Training}
\label{sec:validation}

A validation dataset is needed to prevent overfitting training data, to try
to test how the training data does against real lenses, and to train the
hyperparameters from any priors we might use. These need to come in
two categories: actual lens environments, and simulated lenses. The need for
two sets arises because of the paucity of actual lenses. In \SW, most training
objects are explicitly given to a user -- if a user incorrectly identifies a
training object, they are informed of that failure, and likewise for a correct
classification.

\begin{figure}
\begin{center}
    \includegraphics[scale=]{Figures/}
\end{center}
\caption{This figure }
\label{fig:validation}
\end{figure}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{Dynamic Allocations}
\todo{Chris}{This section will examine whether we would be better off
  dynamically assigning images to people (based on current estimates of skill
  and probability) rather than randomly assigning them. This means I will need
  to create some sort of 'SpaceWarps Emulator'. (Actually, the other thing
  I can do is use the blacklist developed earlier to throw out
  contributions in an informed manner in order to construct different
  simulations.) Before I even do that, another
aspect I would like to examine and is probably useful is whether we can
reliably identify skilled users early on. That is, instead of looking at final
skill vs effort, look at many trajectories of skill vs effort over time. That
would be a useful thing to show to prove that we can find the good users in the
first place -- early on!}
